Projects

### 2024-03-22 qmd/projects.qmd
updated to fit better on mobile

>>>>

```
```{=html}
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Box with Rounded Edges</title>
  <style>
    body {
      margin: 0; /* Remove default margin */
      padding: 0; /* Remove default padding */
    }

    .container {
      width: 100%; /* Adjusted width to fit the screen */
      max-width: 600px; /* Limiting maximum width */
      height: auto; /* Set container height */
      border: 0.5px solid #ccc; /* Light grey color */
      border-radius: 8px; /* Less rounded edges */
      overflow: hidden; /* Hide overflow content */
      margin-bottom: 20px; /* Add margin to create space between rows */
      display: flex; /* Use flexbox for layout */
      align-items: center; /* Center items vertically */
      text-decoration: none; /* Remove underline */
    }

    .image-container img {
      max-width: 100%; /* Ensures the image does not exceed its container */
      height: auto;
      display: block;
      border-radius: 8px; /* Rounded corners for image */
    }

    .text h1 {
      font-size: 22px; /* Adjusted text size */
      margin-top: 0;
      margin-bottom: 5px; /* Adjust margin between large and small text */
      color: black;
    }

    .text h1:hover {
      color: #2068DC; /* Change text color to blue on hover */
    }

    @media (max-width: 768px) {
      .container {
        margin-right: auto; /* Reset margin-right */
        margin-left: auto; /* Reset margin-left */
        flex-direction: column; /* Stack items vertically on smaller screens */
      }

      .content {
        padding: 10px; /* Reduce padding on smaller screens */
      }
    }
  </style>
</head>
```
